Playing Atari with Keras and R

### 2018-07-13 article.Rmd
more on gym

>>>>

```{r}
gym <- import("gym")
env <- gym$make("BreakoutDeterministic-v4")
initial_state <- env$reset()
```

Calling `env$reset()` will return a 3d array with the initial frame of the game.
We can render it by calliing `env$render()`.

With Gym we can also perform actions in the game by using the method `step`.

```{r}
result <- env$step(0L)
```
